Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-06 csf-2017/paper.tex
notation in world theorem
intuition about logical relation

@@

\section{Logical relation}

\begin{itemize}
\item Intuition
\item Worlds
\item Logical relation
\item Fundamental theorem
\item Discussion/comparison with related Dreyer-Neis-Birkedal and with Hur-Dreyer
\end{itemize}

%\begin{theorem}\label{thm:world-existence}
  There exists a \cofe{} $\Wor$ and preorders $\futurestr$ and $\futurewk$ such that $(\Wor,\futurestr)$ and $(\Wor,\futurewk)$ are preordered \cofes{}, and there exists an isomorphism $\xi$ such that
  {\small 
  \begin{align*}
    \xi : \Wor & \cong \blater (\nats \finparfun \Regions)\\
    \Regions & = \{\revoked\} \uplus \\
             &\hskip -2cm \{\temp\} \times \States \times \Rels \times (\States \fun (\Wor \monwknefun \UPred{\HeapSegments})) \uplus \\
            & \hskip -2cm \{\perma\} \times \States \times \Rels \times (\States \fun (\Wor \monstrnefun \UPred{\HeapSegments}))
 \end{align*}
 }
 and for $W, W' \in \Wor$
 \begin{align*}
   W \futurestr W' & \Leftrightarrow \xi(W) \futurestr \xi(W')   \\
   W \futurewk W' & \Leftrightarrow \xi(W) \futurewk \xi(W')
 \end{align*}
%Let $\iota.v$ be the projection of the view of a region.
Worlds are finite partial maps from region names to regions,
and region names are simply natural numbers
\begin{align*}
  \Worlds & = \RegionNames \finparfun \Regions\\
 \RegionNames & = \nats.
\end{align*}
The \emph{private future} region relation satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurestr (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}
The \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurewk (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ (\temp,s,\phi_\pub,\phi,H) \in \Regions }
  { (\temp,s,\phi_\pub,\phi,H) \futurewk \revoked }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

@@

@@

\end{document}
\grid

>>>>

\emph{adversary}: It doesn't sound ``sexy'' to constantly say ``an untrusted
piece of code'' should we adopt the convention that adversary refers
to an unstrusted piece of code?

@@

\section{Logical relation}
In order to be able to reason about programs running on the capability
machine and prove properties such as well-bracketedness and
encapsulation about them, we define a unary logical relation.
%
% Intuition
The logical relation is a semantic models of all the words on the
capability machine that are definitely safe to give to an
adversary. Whether a capability is safe to give to an adversary
depends heavily on the contents of the memory as instructions as well
as capabilities may reside in memory. The memory will be modeled using
worlds where a world can be seen as a collection of protocols that
parts of the memory must satisfy. The memory changes during an
execution as memory is allocated and part of memory changes
purpose. The model needs to be able to express these changes to the
memory which is captured by the future world relations.
%

\subsection{Worlds}
%\begin{theorem}\label{thm:world-existence}
  There exists a \cofe{} $\Wor$ and preorders $\futurestr$ and $\futurewk$ such that $(\Wor,\futurestr)$ and $(\Wor,\futurewk)$ are preordered \cofes{}, and there exists an isomorphism $\xi$ such that
  {\small 
  \begin{align*}
    \xi : \Wor & \cong \blater (\nats \finparfun \Regions)\\
    \Regions & = \{\revoked\} \uplus \\
             &\hskip -2cm \{\temp\} \times \States \times \Rels \times (\States \fun (\Wor \monwknefun \UPred{\HeapSegments})) \uplus \\
            & \hskip -2cm \{\perma\} \times \States \times \Rels \times (\States \fun (\Wor \monstrnefun \UPred{\HeapSegments}))
 \end{align*}
 }
 and for $W, W' \in \Wor$
 \begin{align*}
   W' \futurestr W & \Leftrightarrow \xi(W') \futurestr \xi(W)   \\
   W' \futurewk W & \Leftrightarrow \xi(W') \futurewk \xi(W)
 \end{align*}
%Let $\iota.v$ be the projection of the view of a region.
Worlds are finite partial maps from region names to regions,
and region names are simply natural numbers
\begin{align*}
  \Worlds & = \RegionNames \finparfun \Regions\\
 \RegionNames & = \nats.
\end{align*}
The \emph{private future} region relation satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurestr (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr (\temp,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ r \in \Regions }
  { r \futurestr \revoked }
\end{mathpar}
The \emph{public future} region relations satisfies the following properties:
\begin{mathpar}
  \inferrule{  (s,s') \in \phi_\pub \\
    (v,\phi_\pub,\phi,H) = (v',\phi_\pub',\phi',H')}
  {  (v',s',\phi_\pub',\phi',H') \futurewk (v,s,\phi_\pub,\phi,H) }
  \and
  \inferrule{ (\temp,s,\phi_\pub,\phi,H) \in \Regions }
  { (\temp,s,\phi_\pub,\phi,H) \futurewk \revoked }
  \and
  \inferrule{ }
  { \revoked \futurewk \revoked }
\end{mathpar}

@@

\subsection{Logical relation}

\subsection{Fundamental theorem of logical relations}

\subsubection{Discussion/comparison with related Dreyer-Neis-Birkedal and with Hur-Dreyer}

@@

\bibliographystyle{plainnat}
\bibliography{references}
\end{document}
\grid
